### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
Regmachine: proof-reading done

The following theorem asserts that the event structure built this way
indeed satisfies the axioms of the prime confusion free event structure.

@@

First, we need to show that $\caOrd \ \defeq \ (\lPO \cup \lRF)^*$
is a partial order. Reflexivity and transitivity follows immediately 
from the definition of the reflexive-transitive closure. 
To show antisymmetry note that $\lessdot_{\lPO} \subseteq \identOrd$
and $\lessdot_{\lRF} \subseteq \identOrd$ by construction. 
Therefore $\caOrd \subseteq \identOrd$. Since $\identOrd$ is
partial order, it is antisymmetric, and thus $\caOrd$ should also be antisymmetric.
The axiom of finite cause, \ie $\prefix{e}$ is finite for every event $e$, 
follows from the fact that at each step of the construction 
the set of possible predecessors of the new event 
can be over-approximated by the finite sequence $\eventSeq$.

Second, we need to show that the conflict relation defined as 
$ e_1 \primcfRel e_2 \iff e_1 \neq e_2 \wedge \lfPO(e_1) = \lfPO(e2) $
obeys the laws of primitive conflict relation. 
Trivially, this relation is irreflexive, symmetric, and transitive.
Also, it is easy to see that it satisfies choice-locality. 
The side condition $\neg (e_{\lPO} \cfRel e_{\lRF})$ of the rule \ESLoadRule
ensures that the primitive conflict relation would not violate 
hereditary property.

In \cref{fig:eventstruct-example} one can see the prime event structure
obtained as a result of incremental construction 
depicted in \cref{fig:regmachine-eventstruct-example}.

@@

Once the event structure is constructed, one can extract
the configurations corresponding to the particular runs 
of the parallel register machine, and 
further filter them via \emph{consistency predicate}
defining the \emph{memory consistency model}.
Our construction of the event structures allows to encode 
a wide class of so-called $\lPO\cup\lRF$ acyclic 
relaxed memory models~\cite{Lahav-al:PLDI17}.

>>>>

The following theorem asserts that the event structure built this way
indeed satisfies the axioms of the prime confusion-free event structure.

@@

First, we need to show that $\caOrd \ \defeq \ (\lPO \cup \lRF)^*$
is a partial order. Reflexivity and transitivity follows immediately 
from the definition of the reflexive-transitive closure. 
To show antisymmetry note that $\lessdot_{\lPO} \subseteq \identOrd$
and $\lessdot_{\lRF} \subseteq \identOrd$ by construction. 
Therefore $\caOrd \subseteq \identOrd$. Since $\identOrd$ is
a partial order, it is antisymmetric, and thus $\caOrd$ should also be antisymmetric.
The axiom of finite cause, \ie $\prefix{e}$ is finite for every event $e$, 
follows from the fact that at each step of the construction 
the set of possible predecessors of the new event 
can be over-approximated by the finite sequence $\eventSeq$.

Second, we need to show that the conflict relation defined as 
$ e_1 \primcfRel e_2 \iff e_1 \neq e_2 \wedge \lfPO(e_1) = \lfPO(e2) $
obeys the laws of primitive conflict relation. 
Trivially, this relation is irreflexive, symmetric, and transitive.
Also, it is easy to see that it satisfies choice-locality. 
The side condition $\neg (e_{\lPO} \cfRel e_{\lRF})$ of the rule \ESLoadRule
ensures that the primitive conflict relation would not violate 
the hereditary property.

In \cref{fig:eventstruct-example} one can see the prime event structure
obtained as a result of the incremental construction 
depicted in \cref{fig:regmachine-eventstruct-example}.

@@

Once the event structure is constructed, one can extract
the configurations corresponding to the particular runs 
of the parallel register machine, and 
further filter them via the \emph{consistency predicate}
defining the \emph{memory consistency model}.
Our construction of event structures allows to encode 
a wide class of so-called $\lPO\cup\lRF$ acyclic 
relaxed memory models~\cite{Lahav-al:PLDI17}.
